Well-being of Individuals from the United States Global Social Survey are Affected by Finances, Relationships, and Health

### 2023-03-16 outputs/paper/paper3.qmd
Added all the necessary tables for analysis

```{r}
happycleaned %>% 
  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "cell") %>% 
  add_p()
```

@@

@@

@@

>>>>

```{r}
master_clean5 %>% 
  tbl_cross(row = satfin, col = new_income_range, label = list(new_income_range ~ "Income Ranges", satfin ~ "Financial Satisfaction"), percent = "column")
```
```{r}
happycleaned %>% 
  tbl_cross(row = happy, col = satfin, label = list(satfin ~ "Financial Satisfactions", happy ~ "Happiness"), percent = "column")
```
```{r}
happycleaned %>% 
  tbl_cross(row = happy, col = new_income_range, label = list(new_income_range ~ "Income Ranges", happy ~ "Happiness"), percent = "column")
```

@@

```{r}
hapmarcleaned %>% 
  tbl_cross(row = hapmar, col = satfin, label = list(satfin ~ "Financial Satisfactions", hapmar ~ "Happiness of Marriage"), percent = "column")
```

```{r}
hapmarcleaned %>% 
  tbl_cross(row = hapmar, col = new_income_range, label = list(new_income_range ~ "Income Ranges", hapmar ~ "Happiness of Marriage"), percent = "column")
```

@@

```{r}
healthcleaned %>% 
  tbl_cross(row = health, col = satfin, label = list(satfin ~ "Financial Satisfactions", health ~ "Quality of Health"), percent = "column")
```

```{r}
healthcleaned %>% 
  tbl_cross(row = health, col = new_income_range, label = list(new_income_range ~ "Income Ranges", health ~ "Quality of Health"), percent = "column")
```

@@

```{r}
finaltercleaned %>% 
  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
```

```{r}
finaltercleaned %>% 
  tbl_cross(row = finalter, col = new_income_range, label = list(new_income_range ~ "Income Ranges", finalter ~ "Changes in Wealth"), percent = "column")
```
